The \greentext{plant parameters} are assumed to be known.
\begin{alignat*}{3}
    G&:~    & \dot{x}_p(t) &= \knownVar{a_p} x_p(t)
                    + \knownVar{k_p} \unknownVar{u(t)},
            \tag{\ref{eq:G-linear}}\\
            &&& \txt{IC } x_p(0) \in \R
\end{alignat*}~

Pick $u(t)$ such that the dynamical behaviour
of the closed loop is equal to that of the model.
This is done by comparing \eqn{eq:G-linear} to \eqn{eq:G-des}.
\begin{align*}
u^*(t)
    &= \frac{1}{k_p} \left( -a_p x_p(t) + a_m x_p(t) + k_m r(t) \right)\\
    &= \underbrace{\frac{a_m - a_p}{k_p}}_{a^*} x_p(t)
        + \underbrace{\frac{k_m}{k_p}}_{k^*} r(t)\\
%    &= a^* x_p(t) + k^* r(t) \\
    &= \matr{a^* & k^*} \matr{x_p(t) \\ r(t)}\\
u^*(t)
    &= \bm{\theta}^{*T} \bm{\phi}(t)
%    \numberthis \label{eq:u-perfect-linear}
\end{align*}~

Using this input%
    \footnote{%
        The starred variables with $*$ superscripts represent
        the ideal values of the control parameters.
    }%
, now the dynamics of the plant $G$ matches the dynamics
of the model $M$, as in equation \eqn{eq:G-des}.\\

However, even though now the dynamics are the same,
the initial conditions are not necessarily the same.
Would this input also work for $x_m(0) \neq x_p(0)$?
I.e., does this guarantee that
$x_p(t) \rightarrow x_m(t)$ for $t \rightarrow \infty$?

\paragraph{Dependence on the initial conditions}
To check this, we examine the error dynamics
and see if the error asymptotically goes to zero.
\begin{align*}
e(t) &= x_p(t) - x_m(t)\\
\dot{e}(t) &= \dot{x}_p(t) - \dot{x}_m(t)\\
\end{align*}

Using eqns. \eqn{eq:M} and \eqn{eq:G-des}:
\begin{align}
\dot{e}(t)    &= a_m e(t)
\label{eq:error-dynamics}
\end{align}~

\begin{conclusion}{darkgreen}
If $a_m <0$, the error dynamics are stable.
That is, $e(t) \rightarrow 0$ for any ICs.
\end{conclusion}

\paragraph{Conclusion}
\begin{itemize}
\item Model reference control (MRC) works with the error dynamics of the
    reference model
\item \redtext{We need to know all plant parameters very well} \\
    $\Rightarrow$ Problem: \redtext{uncertainty in parameters}
\end{itemize}
